<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### João Bettencourt

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```


### Normal Cumulative Probabilities
```{r}
pnorm(c(2,2.5), mean=2, sd=0.5, lower.tail=TRUE)
```


```{r}
0.8413447 - 0.5000000
```



### Normal Cumulative Probabilities
```{r}
pnorm(c(0.12), mean=2, sd=0.5, lower.tail=FALSE)
```


### Normal Quantiles
```{r}
qnorm(c(0.12), mean=2, sd=0.5, lower.tail=FALSE)
```


### Uniform Cumulative Probabilities
```{r}
punif(c(5.6,6.4), min=5, max=7, lower.tail=TRUE)
```


### Table of Poisson Probabilities
```{r}
local({
  .Table <- data.frame(Probability=dpois(0:5, lambda=0.8))
  rownames(.Table) <- 0:5 
  print(.Table)
})
```


```{r}
0.449328964 + 0.359463171 + 0.143785269
```



### Exponential Cumulative Probabilities
```{r}
pexp(c(4), rate=0.1, lower.tail=TRUE)
```


### Binomial Cumulative Probabilities
```{r}
pbinom(c(9), size=18, prob=0.45, lower.tail=TRUE)
```


### Table of Binomial Probabilities
```{r}
local({
  .Table <- data.frame(Probability=dbinom(0:18, size=18, prob=0.6))
  rownames(.Table) <- 0:18 
  print(.Table)
})
```



### Uniform Quantiles
```{r}
qunif(c(0.5), min=4, max=6, lower.tail=TRUE)
```


### Uniform Quantiles
```{r}
qunif(c(0.55), min=4, max=6, lower.tail=TRUE)
```


```{r}
qunif(c(0.51), min=4, max=6, lower.tail=TRUE)
```



### Table of Binomial Probabilities
```{r}
local({
  .Table <- data.frame(Probability=dbinom(0:10, size=10, prob=0.3))
  rownames(.Table) <- 0:10 
  print(.Table)
})
```


```{r}
0.0282475249 + 0.1210608210 + 0.2334744405 + 0.2668279320
```


```{r}
((5-4*0)*0.3)+((5-4*1)*0.4)+((5-4*2)*0.2)+((5-4*3)*0.1)
```


```{r}
(((5-4*0)*0.3)+((5-4*1)*0.4)+((5-4*2)*0.2)+((5-4*3)*0.1)^2)
```


```{r}
(((5-4*0)*0.3)^2)+(((5-4*1)*0.4)^2)+(((5-4*2)*0.2)^2)+(((5-4*3)*0.1)^2)
```


```{r}
3.26*1.79
```


```{r}
0.6*0.6
```


```{r}
((5-4*0)*0.3)+((5-4*1)*0.4)+((5-4*2)*0.2)+((5-4*3)*0.1)
```


```{r}
(5-4*0)*0.3
```


```{r}
(5-4*1)*0.4
```


```{r}
1.5*1.5
```


```{r}
(5-4*2)*0.2
```


```{r}
(5-4*3)*0.1
```


```{r}
-0.49 + -0.36 + 0.16 + 2.25
```



### Uniform Cumulative Probabilities
```{r}
punif(c(5.6,6.4), min=5, max=7, lower.tail=TRUE)
```



### Uniform Cumulative Probabilities
```{r}
punif(c(5), min=4, max=6, lower.tail=FALSE)
```

```{r}
punif(c(5), min=4, max=6, lower.tail=TRUE)
```



### Normal Cumulative Probabilities
```{r}
pnorm(c(5), mean=4, sd=6, lower.tail=FALSE)
```

